\documentclass[12pt,a4paper]{article}

%Packages

\usepackage[margin=1in]{geometry}   % Page margins
\usepackage{setspace}               % Line spacing
\usepackage{titlesec}               % Section formatting
\usepackage{lmodern}                % Improved font
\usepackage{hyperref}               % Clickable references
\usepackage{enumitem}               % Better lists

%Formatting
\onehalfspacing                      % 1.5 line spacing
\setlength{\parindent}{0pt}          % No paragraph indentation
\setlength{\parskip}{6pt}            % Space between paragraphs

\titleformat{\section}
  {\normalfont\Large\bfseries}
  {\thesection}{1em}{}

%Document Info

\title{\textbf{Esoteric Programming Languages}}
\author{u23718146 \\ Shavir Vallabh}
\date{\today}

%Beginning of document
\begin{document}

\maketitle
\vspace{1em}

\section{Question One}

An \textit{esoteric programming language}, or \textit{'esolang'}, refers to a type of programming language designed to be unconventional and unlike traditional programming languages. They feature purposefully obfuscated syntax, unique compilation/interpretation processes, and generally aim to push the boundaries of language design into the realm of art. 
\section{Question Two}

\textit{Esolangs} have limited application in the same context as traditional programming languages, but that is not to assert that they have no practical applications.

\begin{enumerate}
    \item \textbf{Educational Value}
    \newline By stripping languages down to their bare essentials, they can aid in understanding memory models, compilation, and control flow with little to nothing in the way, unlike traditional languages.
    
    \item \textbf{Artistic Expression}
    \newline Some \textit{esolangs} treat code as a performative or artistic work, such as \textit{\href{https://github.com/your-diary/piet_programming_language/blob/master/README.md}{Piet}}, a visual language in which programs look like abstract, cubist paintings.
    
    \item \textbf{Security Potential}
    \newline Due to inherent code obfuscation, some languages like \textit{\href{https://jsfuck.com/}{JSFuck}} easily get past traditional malware detection. The opposite can also be done, sensitive code could theoretically have a built-in layer of 'encryption' by utilizing them.

    \item \textbf{Compiler/ Interpreter Research}
    \newline Some \texit{esolangs} feature unique compilation and interpretation processes. These can help contribute to understanding of the compilation process, and provide insights from a fresh angle. One example of this is \textit{\href{https://dgtools.readthedocs.io/en/latest/brainfuck.html}{Brainfuck}}, which was designed to have the smallest possible compiler fort he \textit{AmigaOS}.
    
\end{enumerate}

\section{Question Three}

\begin{enumerate}
    \item \textbf{}
    
\end{enumerate}

\section{Question Four}
% Content to be added

\section{References}
\begin{enumerate}
    \item Jeremy Singer and Steve Draper (2025) (PDF) let’s take esoteric programming languages seriously. Available at: \url{https://www.researchgate.net/publication/391953647\_Let’s\_Take\_Esoteric\_Programming\_Languages\_Seriously} (Accessed: 22 February 2026). 
\end{enumerate}


\begin{itemize}[leftmargin=1.5em]
    \item Author, \textit{Title of Source}, Publisher or Website, Year.
    \item Author, \textit{Title of Source}, Publisher or Website, Year.
\end{itemize}

\end{document}
